Participatory Mashups: Using Users to make Data Mashable

### 2008-09-20 papers/cscw_mash/cscw_mash.tex
Spell check. This is the submitted version.

Some kinds of information are easier to understand than others, and mashups have so far understandably focussed on the low-hanging fruit. Addresses follow an easily recognized pattern, and have led to a large number of useful mashups which plot various things on maps or work out what things are near to other things. Similarly, many mashups have made use of data that is available from APIs, or that can be easily scraped from popular web pages that the mashup has been hard-coded to understand.

@@

As a user browses the web, Think Link highlights snippets of text that other users have identified as making claims that are interesting or contraversial (Figure~\ref{highlight}). Interesting claims are highlighted in yellow, and contraversial claims are highlighted in red. If a user clicks on a highlighted snippet, Think Link will display an interface that allows a user to easily find snippets on other web pages that make related claims, including snippets that argue against the opinion put forward by the highlighted snippet (Figures~\ref{claimview} and \ref{claimbrowse_diagram}). Think Link allows a user to easily access the best arguments for and against a claim, including arguments they might not otherwise have come across because they would not have been voiced by the web sites that the reader normally reads.

@@

As views a web page, Mash Maker will suggest ways that it can make the page more useful, and suggest these improvements on its toolbar. If the user clicks on the button for such an improvement then Mash Maker will apply it to the current page, potentially using other web sites and remote APIs, and potentially applying widgets that produce new visualizations or compute new data (Figure~\ref{mapinsert}). Mash Maker suggests improvements based on the meaning of the current page, the meaning of pages that the user has recently browsed, and the behaviour of other users.

Our intention is that users should be able to use Mash Maker to enhance arbitrary web sites in arbitrary ways. Unlike ``mashup creation tools'' like Yahoo Pipes~\cite{pipes} or Microsoft Popfli~\cite{popfly}, we see Mash Maker not a tool for creating special-case mashup sites, but as a generalized tool that understands what you are doing and infers new mashups that can enhance your current experience, based on what others have tried in the past.

@@

Users teach Mash Maker ``patterns'' that Mash Maker can use to understand a large number of similarly formatted web pages (e.g. how to understand a flight listing on expedia). This differs from Think Link, in which users pick out individual instances of factual claims which are not generalized to automatically find more snippets.

@@

reCAPTCHA~\cite{recaptcha} gives users the task of correctly transcribing scanned books as a test to see if they are human. Users thus unintentionally help machines better understand this information. Luis von Ahn has also shown how users can be persueded to teach a system what data means by making it fun~\cite{vonahn}. Our approach to persueding users to teach us what data means is to make this data immediately useful to them.

@@

Like Think Link, SpinSpotter~\cite{spinspotter} also uses a browser plugin to help users identify and share instanes of media bias and misrepresentation. SpinSpotter allows users to annotate web pages with comments about the spin they think is present and suggest textual edits. This differs from Think Link, which attempts to understand what claims are being made and relate them to claims made elsewhere on the web.

>>>>

Some kinds of information are easier to understand than others, and mashups have so far understandably focused on the low-hanging fruit. Addresses follow an easily recognized pattern, and have led to a large number of useful mashups which plot various things on maps or work out what things are near to other things. Similarly, many mashups have made use of data that is available from APIs, or that can be easily scraped from popular web pages that the mashup has been hard-coded to understand.

@@

As a user browses the web, Think Link highlights snippets of text that other users have identified as making claims that are interesting or controversial (Figure~\ref{highlight}). Interesting claims are highlighted in yellow, and controversial claims are highlighted in red. If a user clicks on a highlighted snippet, Think Link will display an interface that allows a user to easily find snippets on other web pages that make related claims, including snippets that argue against the opinion put forward by the highlighted snippet (Figures~\ref{claimview} and \ref{claimbrowse_diagram}). Think Link allows a user to easily access the best arguments for and against a claim, including arguments they might not otherwise have come across because they would not have been voiced by the web sites that the reader normally reads.

@@

As views a web page, Mash Maker will suggest ways that it can make the page more useful, and suggest these improvements on its tool bar. If the user clicks on the button for such an improvement then Mash Maker will apply it to the current page, potentially using other web sites and remote APIs, and potentially applying widgets that produce new visualizations or compute new data (Figure~\ref{mapinsert}). Mash Maker suggests improvements based on the meaning of the current page, the meaning of pages that the user has recently browsed, and the behavior of other users.

Our intention is that users should be able to use Mash Maker to enhance arbitrary web sites in arbitrary ways. Unlike ``mashup creation tools'' like Yahoo Pipes~\cite{pipes} or Microsoft Popfly~\cite{popfly}, we see Mash Maker not a tool for creating special-case mashup sites, but as a generalized tool that understands what you are doing and infers new mashups that can enhance your current experience, based on what others have tried in the past.

@@

Users teach Mash Maker ``patterns'' that Mash Maker can use to understand a large number of similarly formatted web pages (e.g. how to understand a flight listing on Expedia). This differs from Think Link, in which users pick out individual instances of factual claims which are not generalized to automatically find more snippets.

@@

reCAPTCHA~\cite{recaptcha} gives users the task of correctly transcribing scanned books as a test to see if they are human. Users thus unintentionally help machines better understand this information. Luis von Ahn has also shown how users can be persuaded to teach a system what data means by making it fun~\cite{vonahn}. Our approach to persuading users to teach us what data means is to make this data immediately useful to them.

@@

Like Think Link, SpinSpotter~\cite{spinspotter} also uses a browser plugin to help users identify and share instances of media bias and misrepresentation. SpinSpotter allows users to annotate web pages with comments about the spin they think is present and suggest textual edits. This differs from Think Link, which attempts to understand what claims are being made and relate them to claims made elsewhere on the web.
